cover letter

### 2023-03-17 paper/admin/cover_letter.tex
final round of edits before submission
title change

\newcommand{\journal}{Nature Neuroscience}
\newcommand{\articletype}{Article}
\newcommand{\myTitle}{High-order cognition is supported by information-rich but compressible brain activity patterns}
\newcommand{\corresponding}{Jeremy R. Manning}

@@

  We developed a computational framework for evaluating our two measures of
  interest (informativeness and compressibility), and we applied the framework
  to a public fMRI dataset. In the dataset's experiment, participants either
  listened to an auditory recording of a story, listened to temporally
  scrambled recordings of the story (randomizing the orders of paragraphs or
  words), or underwent a resting state scan. Each condition is designed to
  engage cognitive processing and engagement at different depths. For example,
  listening to the intact story leads participants to mentally engage with the
  narrative, and to deeply process and connect narrative events in a way that
  leads to a rich understanding of the story. Listening to temporally scrambled
  versions of the story might lead to understanding invidual paragraphs or
  words. However, individual moments in the temporally scrambled stories lack
  contextual elements that enable participants to gain a deeper understanding.
  Across conditions, we found that both informativeness and compressibility of
  the brain patterns changed systematically with the cognitive ``richness'' of
  the stimulus across the different experimental conditions. We also traced out
  the brain networks associated with these changes. We found that networks
  traditionally associated with higher-level cognitive functions tended to
  exhibit more information-rich brain patterns than networks traditionally
  associated with lower-level cognitive functions.

>>>>

\newcommand{\journal}{Nature Neuroscience}
\newcommand{\articletype}{Article}
\newcommand{\myTitle}{High-level cognition is supported by information-rich but compressible brain activity patterns}
\newcommand{\corresponding}{Jeremy R. Manning}

@@

  We developed a computational framework for evaluating our two measures of
  interest (informativeness and compressibility), and we applied the framework
  to a public fMRI dataset. In the dataset's experiment, participants either
  listened to an auditory recording of a story, listened to temporally
  scrambled recordings of the story (randomizing the orders of paragraphs or
  words), or underwent a resting state scan. Each condition is designed to
  engage cognitive processing and engagement at different depths. For example,
  listening to the intact story leads participants to mentally engage with the
  narrative, and to deeply process and connect narrative events in a way that
  leads to a rich understanding of the story. Listening to temporally scrambled
  versions of the story might lead to understanding individual paragraphs or
  words. However, individual moments in the temporally scrambled stories lack
  contextual elements that enable participants to gain a deeper understanding.
  Across conditions, we found that both informativeness and compressibility of
  the brain patterns changed systematically with the cognitive ``richness'' of
  the stimulus across the different experimental conditions. We also traced out
  the brain networks associated with these changes. We found that networks
  traditionally associated with higher-level cognitive functions tended to
  exhibit more information-rich brain patterns than networks traditionally
  associated with lower-level cognitive functions.
